\documentclass[12pt]{article}

\usepackage{mathtools} 
\usepackage{cite}
\usepackage{graphicx}

\begin{document}
\section{Progress}
\begin{itemize}
\item Collected papers regarding Hilbert space filling curves. The algorithms are space filling curves, not Hilbert space filling curves because they are not recursive. This needs a decision about pursuing this further. Peano curves are related
\item Code provided to Kanika to select N samples from $\Pi_{i=0}^{x} V_i*D_i$ using a simple space filling curve. This produced a smooth even sample curve between each of the dimensions, it also suffered from over sampling from a single variable $V_i$ and from that single variables domain $D_i$ when the step size is one of the dimensional sizes.

\item Reorganized Thesis documents into master documents and sub documents so future organization is easier. Appendix enhanced with updated references and bib tex entries. There are some X entries in the references section now. 
\item Reading either a paper (related) or several articles (unrelated) each night for background material. Working on skimming and marking up with highlighter as quick practice. 
\end{itemize}
\section{Other Work}
\begin{itemize}
\item Produced a report of the project description for Dr. Catherine Page.  Also provided background material and asked her to sit on the dissertation board should I be accepted into the PhD. program.  
\item http://chemistry.uoregon.edu/profile/cpage/
\item Potentially investigating how this project would benefit from AI/ML in the long run. If so then taking the project in that direction so Dr. Daniel Loud  
\item Hopefully won a bid for work from my old employer. Contract work that should take about a day hopefully.
\end{itemize}
\newpage
\section{Questions}
\begin{itemize}
\item I feel like I've stalled with Thesis as I don't know what to write about or research next. I still think a survey paper of the internal representation techniques currently used is the right way to go. Will this demonstrate the ability to research the background of a subject thoroughly?
\item Programmatic generation of a hypergraph is not standard and should not be the qualifying criteria for a hypergraph/graph package in the rest of the world, leaving this custom development to explore it. Would a qualitative report capture the essence that these software packages are not capable of dealing with the representation? 
\item On the current trajectory will be I be in place to get into a PhD. program at the University of Oregon?
\end{itemize}

\section{Decision}
\begin{itemize}
\item If i am in place to get into a PhD. program the deadline for application is Dec 10th, I need to possibly take the GRE again which will consume the current time spent on Thesis work to study for the GRE and take the test.
\item If I do not need to re-take the GRE then I can spend more time working on Thesis. 
\end{itemize}


\end{document}