\documentclass[12pt]{article}
\usepackage{hyperref} 
\usepackage{mathtools} 
\usepackage{cite}
\usepackage{graphicx}

\begin{document}
\section{Week 8}
\begin{itemize}
	\item Space filling curves have proven to improve performance of memory access by magnitudes \href{https://arxiv.org/pdf/1606.06133.pdf}{https://arxiv.org/pdf/1606.06133.pdf} June 2016, Nico Reissmann, Magnus Jahre, Jan Christian Meyer, HPC Section, IT Dept. NTNU, Norway
	\item Performance analysis of SFC, specifically the sampling of random points in the space. Hilbert wins. \href{https://math.dartmouth.edu/~ddeford/icpp13.pdf}{https://math.dartmouth.edu/~ddeford/icpp13.pdf}
	\item Reordering instructions via Hilbert curve, indexing along the curve, circa 2000/2002\\ \href{http://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.65.1757&rep=rep1&type=pdf}{http://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.65.1757\&rep=rep1\&type=pdf}
	
	\item Customization of SFC to solve the particular problem at hand. Circa 2001 on multiple applications. \href{https://www.cerias.purdue.edu/assets/pdf/bibtex_archive/p512-mokbel.pdf}{http://...mokbel.pdf}
	\item How do I access this and related articles? I've contacted the ACM about this. 
	\href{http://dl.acm.org/citation.cfm?id=1366223}{http://dl.acm.org/citation.cfm?id=1366223}
	\item Sierpinski space-filling curves applied to create a representation that can be reasoned over \href{http://delivery.acm.org/10.1145/2950000/2947668/a19-meister.pdf?ip=71.210.18.67\&id=2947668\&acc=OPEN\&key=4D4702B0C3E38B35%2E4D4702B0C3E38B35%2E097C819FD0D4FEF9%2E6D218144511F3437&CFID=694001933&CFTOKEN=39857927&__acm__=1479277565_87c43d68c57fdd45bfa83ddcef0eed42}{a19-meister.pdf}
\end{itemize}

\section{Personal Life}
\begin{itemize}
	\item Contract job for Datalogic complete. Windows hardware qualification of kernel mode drivers certified and distributed. Invoice delivered. 
	\item AI is difficult but fascinating. Homework has been challening and exciting to complete, I've spent to much time on this class. This is mostly due to python familiarity and workstation environment. 
	\item Workstation setup at home and school revamped to increase productivity (Dual monitor, ergo keyboard, mouse, etc.). Development on a laptop was slowing down performance.
	\item Home life has been difficult recently as the new baby Avalyn requires lots of time. Rosalyn has also needed extra time as she adjusts. 
\end{itemize}

\end{document}