\documentclass[12pt]{article}
\usepackage{cite}
\usepackage{url}


\begin{document}

\begin{center}
\section*{Nomination for Dr. Boyana Norris in Outstanding Mentorship in Graduate Studies\\}	
\end{center}

I am excited to be under the guidance of Dr. Boyana Norris and delighted to nominate her for this award. I will graduate in Spring 2017 with a Masters in Computer Science and begin studies as a Ph.D. student in Fall 2017, both under her mentorship. I have enjoyed the time under her instruction and am looking forward to the coming years.\\

Dr. Norris has shown extreme dedication to her graduate students by working countless hours above and beyond the call of duty to ensure they succeed with their research publications. As a mentor in graduate studies she has consistently selected the projects to investigate, publications to pursue, research to perform, and the people to achieve individual and group success.\\

I entered graduate studies with a strong engineering background as opposed to a research affiliation. After 9 years of dedicated software engineering, 2 while going to school and learning from Dr. Norris, I decided to return as a full time student. In January I received and gladly signed the acceptance letter for the Ph.D. in CIS program under Dr. Norris' direction.\\

My mentorship story begins as follows: I wanted to make better renewable batteries. Dr. Norris taught me the techniques to uncover that the research I wanted to do had already been done. Dr. Norris explained how Ph.D. research allows extensive depth of knowledge to be gained via specialization. She quickly had me back on my feet with plans for the future by explaining how I could still contribute to science in a different way. I recommend Dr. Boyana Norris for this award in outstanding mentorship in graduate studies.\\



\noindent
Roscoe Secondo Casita\\
M.S. Computer Information Science (*Pending)\\
Software Engineer III\\
B.S. Computer Software Engineering Technology\\
A.S. Computer Hardware Engineering Technology\\
Minor Applied Mathematics\\
Eagle Scout\\

\end{document}